Centralized Programming for Distributed Control Planes

### 2016-01-26 paper/evaluation.tex
add loc count to eval section.

Not counting the lines for various definitions like prefix and customer groups, which we cannot reveal because of confidentiality concerns, the \sysname policies were \todo{x} lines for the backbone network and \todo{y} lines for the data center networks.

>>>>

Not counting the lines for various definitions like prefix and customer groups or for ownership constraints that define where routes originate, which we cannot reveal because of confidentiality concerns, the \sysname policies were 43 lines for the backbone network and 31 lines for the data center networks.
